### 2019-11-05 submission/manuscript.Rmd
Generate data and viz for first results paragraph

***Results.*** 600 words
Sample description
* Logic for selecting studies (Table S1)
* Distribution of sequence counts across samples in each study (Figure S1)

@@

Change in inter-sample variation with removal of rare sequences
* Increased variation between samples as you remove sequences
* Repeat when sequences are randomized across samples to maintain marginal sums

>>>>

***Results.*** 600 words
Sample description
* Logic for selecting studies (Table S1)

Description / N Samples / N Reads / Median / IQR/Range / Reference

* Distribution of sequence counts across samples in each study (Figure S1)

@@

Change in inter-sample variation with removal of rare sequences
* Increased variation between samples as you remove sequences
* Repeat when sequences are randomized across samples to maintain marginal sums
* Loss of statistical power when rare sequences are removed/no impact on type 1 errors
